---
title       : National Anthems
subtitle    : Music Artist Popularity by Country
author      : Aakash Jain
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## What it does

National Anthems is a webapp that shows you the most popular music artists in
a country, giving you a glimpse into regional trends.

It uses data from Last.FM, a widely used social network for music 
lovers that also keeps track of what its users listen to.

It is made in R with the Shiny framework, as part of a project for the
Developing Data Products course on Coursera.

---

## Scraping the Last.FM API

Last.FM exposes records through a web API that can be very simply scraped.
For example, to get data for the top 5 artists among US users:

```{r}
require(httr)
require(knitr)
request <- POST('http://ws.audioscrobbler.com/2.0/',
              body=list(method='geo.getTopArtists',
              api_key='4d1e099188a7028fad88d7bd0ac7353d',
              country='United States', limit=5, format='json'),
              encode='form')
stop_for_status(request)
data <- content(request)
```

---

Details for the top artist:

```{r}
data$topartists$artist[[1]]$name
data$topartists$artist[[1]]$listeners
```

After some reshaping, the rCharts package plots the data:

```{r echo=FALSE, results='hide'}
temp <- matrix(nrow=0, ncol=2)
for(i in 1:5) {
  a <- data$topartists$artist[[i]]$name
  l <- data$topartists$artist[[i]]$listeners
  temp <- rbind(temp, c(a, l))
}
data <- as.data.frame(temp, stringsAsFactors=FALSE)
colnames(data) <- c('Artist', 'Listeners')
```
```{r results='hide'}
require(rCharts)
p <- dPlot(y='Artist', x='Listeners', groups='Artist',
              data=data, type='bar')
p$xAxis(type='addMeasureAxis', outputFormat='#,')
p$yAxis(type='addCategoryAxis')
```

---

If the plot does not appear, please refresh the page. This is a problem with the way dimple plots are rendered.

```{r results='asis', echo=FALSE}
p$show()
```

